---
title: "Basic_R_Commands"
author: "Venkat"
date: "2024-01-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

CTRL+L --> clears the console logs

To list the alphabets --> letters
To list the alphabets in uppercase --> LETTERS

To list the months name in an year (fully qualified name)--> month.name
To list the months name in an year (short form abc) --> month.abb

Data Types:
==========

1. INTEGER
2. NUMERIC
3. CHARACTER
4. LOGICAL
5. COMPLEX

# Type checking and type conversion

```{r}
a <- 10
# Check the datatype -> typeof(object_name)
print(typeof(a))

# To verify the data --> is_object_name()
print(is.double(a))
#To convert the datatype to another type --> as.data_type(object_name)

print(as.integer(a))
```




Objects:
========
1. vector --> Ordered collection of  basic datatypes. All the elements are of same datatype.

ages <- c(21, 23, 12, 26)
# Here, ages is a numerical vector. 
2. List --> Ordered collection of objects. It can contain a vector, matrix, complex vector, character array, function ...
ids = c(1,2,3,4)
emp.names = c("venkat", "Sairam", "Venkata Sairam Yanamandra")

emp = list(id = ids, names=emp.names)
print(emp$names) ## Only prints the emp names.
print(emp)## Prints the empyloyee details
print(emp[1]) # prints the employee ids
print(emp[[1]][1]) ## prints the first employee id.

emp['location'] = "Visakhapatnam" ## Creates a new element location with given value.

To concatenate two lists --> c(list2, list1)


3. Dataframe --> 
